---
title: "2018-06-01 Stapleton qPCR"
author: "Michael Byrd"
output: html_document
---
##Loading packages
If you do not already have the qpcR library installed in your R, please uncomment the top line and install before running the rest of the code.
```{r, warning = F, message = F}
#install.packages("qpcR")
library(qpcR)
```
##Reading in data
The data is hosted on my Github so that this code can be run from other machines than my own.
```{r}
hex <- read.csv(file = "2018_06_01_qPCR.csv")
```
##Starting with the Analysis
This is where I generate the models for all of the runs included. 
```{r, results='hide'}
m <- modlist(x = hex, cyc = 1, model = l4, remove = "none")
```
Calculating the efficiencies of all the models. I had issues with a few cells, so their errors are reported along with which index of the modlist was associated with them.
```{r}
heff = lapply(1:length(m),function(x){
  tryCatch(
    efficiency(m[[x]],plot = FALSE)
    , error = function(e) print(c(e,x))
  )
})
```
This is where we explicitly extract the critical points of the first and second derivatives of the models
```{r}
hcpd1 = vector(); hcpd1 = lapply(1:length(heff),function(x){
  hcpd1 = c(hcpd1, heff[[x]]$cpD1)
})
hcpd1 = unlist(hcpd1)

hcpd2 = vector(); hcpd2 = lapply(1:length(heff),function(x){
  hcpd2 = c(hcpd2, heff[[x]]$cpD2)
})
hcpd2 = unlist(hcpd2)
```
##Generating output
We bind the cpD1 and cpD2 results into a dataframe. We also remove the first column. Finally we write a csv output file.
```{r}
eff.frame = as.data.frame(rbind(hcpd1,hcpd2))
colnames(eff.frame) = colnames(hex)[-1]; rownames(eff.frame) = c("cpD1","cpD2")
write.csv(eff.frame, file= "2019_01_01_qPCR_output.csv")
```